>

### 2024-09-05 docs/article.qmd
Report the descriptive polypharmacy category #25

tar_read(res_tbl_patient) |>
  dplyr::mutate(
    "year"       = as.character(year),
    "Total"      = n_male + n_female,
    "male"       = sprintf("%s (%s)", prettyNum(n_male,   big.mark = ","), scales::percent(p_male)),
    "female"     = sprintf("%s (%s)", prettyNum(n_female, big.mark = ","), scales::percent(p_female)),
    "male_age"   = sprintf("%.2f (%.2f)", age_male, age_sd_male),
    "female_age" = sprintf("%.2f (%.2f)", age_female, age_sd_female)
  ) |>
  dplyr::select(year, male, female, Total, male_age, female_age) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    year       = "Year",
    male       = "Male",
    female     = "Female",
    male_age   = "Male",
    female_age = "Female"
  ) |>
  flextable::add_header_row(
    values    = c("", "Number of Patients (%)", "Mean Age (SD)"),
    colwidths = c(1, 3, 2),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "all") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::line_spacing(space = 0.7, part = "all")

>>>>

tar_read(res_tbl_patient) |>
  dplyr::mutate(
    "year"       = as.character(year),
    "Total"      = n_male + n_female,
    "male"       = sprintf("%s (%s)", prettyNum(n_male,   big.mark = ","), scales::percent(p_male)),
    "female"     = sprintf("%s (%s)", prettyNum(n_female, big.mark = ","), scales::percent(p_female)),
    "male_age"   = sprintf("%.2f (%.2f)", age_male, age_sd_male),
    "female_age" = sprintf("%.2f (%.2f)", age_female, age_sd_female)
  ) |>
  dplyr::select(year, male, female, Total, male_age, female_age) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    year       = "Year",
    male       = "Male",
    female     = "Female",
    male_age   = "Male",
    female_age = "Female"
  ) |>
  flextable::add_header_row(
    values    = c("", "Number of Patients (%)", "Mean Age (SD)"),
    colwidths = c(1, 3, 2),
    top       = TRUE
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1, align = "left", part = "all") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  flextable::autofit(add_w = 0, add_h = 0) |>
  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))

```{r tbl-res-poly}
#| tbl-cap: Summary statistics of different psychiatric polypharmacy categories

tar_read(res_tbl_poly) |>
  dplyr::mutate(
    "year" = as.character(year),
    "mean_sd" = sprintf("%.2f [%.2f]", mean, sd),
    "median_iqr" = sprintf("%.2f (%.2f)", median, IQR)
  ) |>
  dplyr::select(type:medication, sum, mean_sd) |>
  tidyr::pivot_wider(names_from = type, values_from = c(sum, mean_sd)) |>
  dplyr::select(year, medication, sum_same, sum_multi, mean_sd_same, mean_sd_multi, dplyr::contains("total")) |>
  flextable::flextable() |>
  flextable::set_header_labels(
    year = "Year",
    medication = "Medication",
    sum_same = "Same-class",
    sum_multi = "Multi-class",
    mean_sd_same = "Same-class",
    mean_sd_multi = "Multi-class",
    sum_total = "N",
    mean_sd_total = "Mean [SD]"
  ) |>
  flextable::add_header_row(
    values    = c("", "Population Level (N)", "Per Person (Mean [SD])", "Total Polypharmacy"),
    colwidths = c(2, 2, 2, 2),
    top       = TRUE
  ) |>
  flextable::footnote(
    i = 1,
    j = c(3, 5),
    ref_symbols = c("1", "2"),
    part = "header",
    value = flextable::as_paragraph(
      c(
        "The total occurrence of polypharmacy on the population level/perscription-day",
        "The expected occurrence of polypharmacy per person/perscription-day",
        "Prescription day is defined as the number of prescribed medication per day"
      )
    )
  ) |>
  flextable::align(align = "center", part = "all") |>
  flextable::align(j = 1:2, align = "left", part = "all") |>
  flextable::fontsize(size = 7, part = "all") |>
  #flextable::font(fontname = "Times", part = "all") |>
  flextable::width(j = c(1:8), c(1, rep(1.8, 7)), unit = "cm") |>
  flextable::set_table_properties(opts_pdf = list("arraystretch" = 1, "tabcolsep" = 0))
